G2GML: Graph to Graph Mapping Language for Bridging RDF and Property Graphs

### 2020-03-21 paper.tex
Updates from Overleaf

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{hyperref}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
\newtheorem{defi}[theorem]{Definition}
%
\title{G2GML: Graph to Graph Mapping Language for Bridging RDF and Property Graphs}
%
\titlerunning{G2GML: Graph to Graph Mapping Lanugage}
%\titlerunning{Interoperable Use of RDF and Property Graph}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Hirokazu Chiba\inst{1} \and Ryota Yamanaka\inst{2} \and Shota Matsumoto\inst{3}}
%
\authorrunning{H. Chiba {\itshape et al.}}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Database Center for Life Science, Chiba 277-0871, Japan\\
\email{chiba@dbcls.rois.ac.jp}
\and
Oracle Corporation, Bangkok 10500, Thailand\\
\email{ryota.yamanaka@oracle.com}
\and
Lifematics Inc., Tokyo 101-0041, Japan\\
\email{shota.matsumoto@lifematics.co.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% The abstract should briefly summarize the contents of the paper in 15--250 words.
How can we maximize the value of accumulated RDF data? Although increasing amounts of scientific and social data are described as RDF, their use cases are still limited. Allowing access to the RDF datasets through various interface beyond the SPARQL interface will be expected. Importing the RDF datasets into various graph analysis engines will increase the values of the datasets.  
However, interoperable management of such graph data is challenging due to the differences in existing models and formats depending on various implementations. Here, we redefine the property graph model incorporating the differences in existing models and propose exchangeable serialization formats for property graphs, which can be converted into specific formats for each of the databases. 
The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
We further propose a framework for mapping RDF graphs to property graphs on the basis of the Graph to Graph Mapping Language (G2GML). Using this framework, accumulated graph data described in RDF can be converted to property graphs, which can then be loaded into several graph database engines for further analysis. 
%This work provides interoperability not only between property graph formats but also between RDF and proper graphs.
%Future works include implementing and utilizing graph algorithms to make the most of the accumulated data in various analytical engines.

@@

@@

G2GML is a declarative language, where patterns of RDF and property graphs are described. RDF pattern is described using SPARQL pattern, and property graph pattern is described using Cypher pattern.

\subsubsection{Preliminaries}

An RDF triple $(s, p, o)$ is an element of $(I \cup B) \times I \times (I \cup B \cup L)$ where $I$, $L$ and $B$ are a set of IRIs, a set of literals and a set of blank nodes, which are considered pairwise disjoint. In this paper, an RDF triple is simply called a triple. For a triple $(s, p, o)$, $s$ is called the subject, $p$ the predicate and $o$ the object. An RDF graph is defined as a finite set of triples.

\subsubsection{G2GML}
G2GML describes maps from RDF graphs to Property graphs.

In this paper, we call maps written in G2GML as \textit{G2G maps}.
A \textit{G2G map} consists of one or more \textit{node maps} and \textit{edge maps}.
A \textit{node map} is a function that maps from an RDF graph to a set of \textit{PG nodes}. 
An \textit{edge map} is a function that maps from an RDF graph to a set of \textit{PG edges}.

A node map is described as a pair of (i) a template of a PG node and (ii) an RDF graph pattern that can be written as \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).

\begin{defi}[PG node template]
%\leavevmode \vspace{1mm} \\
\emph{Syntax of PG node template.}
\begin{scriptsize}
\begin{verbatim}
<node_template> ::= "(" node_resource  ":" label  ("{" <property_list> "}")? ")"
<property_list> ::= <property> "," <property_list> | <property>
<property> ::= key":" value
\end{verbatim}
\end{scriptsize}
\end{defi}

A PG node template specifies nodes, labels and properties to be generated by the map. A \texttt{node\_resource} specifies ID of the generated node, which is replaced by the resource retrieved by RDF graph. A \texttt{label} specifies the label of the resultant node. A \texttt{label} also works as the name of node map which is referred from other edge maps.
A \texttt{property} is a pair of \texttt{key} and \texttt{value} that describes properties of nodes.
Note that \texttt{node\_resource} and \texttt{value} are  placeholders of the map replaced by resources or literals retrieved from RDF graphs. On the other hand, \texttt{label} and \texttt{key} must be fixed value.

RDF graph pattern specifies which resources should be mapped to nodes of property graphs. Resources match with these pattern yield solution sets of SPARQL SELECT query, that is, variables and bindings.
The solution sets are mapped to nodes embedding bindings to its corresponding location according to the preciding node map.

The URL bound to \texttt{node\_resource} used as the primary key of the map. Other resources or literals bound to \texttt{value} are concatenated into an array in the manner of \texttt{group\_concat} in SPARQL. is interpreted as a map from a solution of SPARQL query to a tuple of a node, its label and its properties.

\begin{defi}[PG edge template]
%\leavevmode \vspace{1mm} \\
\emph{Syntax of PG edge template.}
\begin{scriptsize}
\begin{verbatim}
<edge_template> ::= "(" src_resource  ":" src_label ")" - 
                    "[" edge_resource?  ":" edge_label  ("{"<property_list> "}")? ")" 
                    (-> | -) "(" dst_resource  ":" dst_label ")"
\end{verbatim}
\end{scriptsize}
\end{defi}

A PG edge template specifies edges, the label, the properties and the source nodes and the destination nodes. A \texttt{src\_resource} and a \texttt{dst\_resource} specify which RDF resource should be mapped to endpoint nodes of resultant edges.
A \texttt{src\_label} and a \texttt{dst\_label} work not only as labels of resultant nodes but also work as implicit constraints of the map.
The resultant source nodes and edge nodes must match patterns in corresponding node maps.
For this reason, \texttt{src\_label} and \texttt{dst\_label} must be defined in other node maps.
A \texttt{edge\_resource}, a \texttt{edge\_label} and a \texttt{property\_list} can be described in the same manner as those counterparts in a node map.

The primary key of an edge map is the tuple of the variable bound to \texttt{src\_resource}, \texttt{edge\_resource} and \texttt{dst\_resource}. As well as node maps, other values of variables bound in \texttt{property\_list} are concatenated into an array.

The resultant edge can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge part and a destination part, the edge will be directed edge.

@@

\begin{defi}[PG Format]
\leavevmode \vspace{1mm} \\
\emph{EBNF notation of the PG format.}
\begin{scriptsize}
\begin{verbatim}
    PG         ::= (Node | Edge)+
    Node       ::= NODE_ID Labels Properties NEWLINE
    Edge       ::= NODE_ID Direction NODE_ID Labels Properties NEWLINE
    Labels     ::= Label*
    Properties ::= Property*
    Label      ::= ':' STRING
    Property   ::= STRING ':' Value
    Value      ::= STRING | NUMBER
    Direction  ::= '--' | '->'
\end{verbatim}
\end{scriptsize}
\end{defi}

@@

%%%%%%%%%%%%%%%%%%%
\section{Use Cases}

We  present several use cases to show the usefulness of G2G mapping framework, where we use publicly available open data available in RDF through SPARQL endpoint.

@@

\begin{figure}[!t]
\vspace{2mm}
\begin{scriptsize}
\begin{verbatim}

@@

\end{verbatim}
\end{scriptsize}
\caption{G2GML for Wikidata extraction}
\label{fig:g2gml_wikidata}
\end{figure}

@@

%In this section, we briefly explain the syntax of G2GML with an example.

%\subsection{Usecase}

@@

%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Evaluation}

% The goal of our evaluation is to observe the impact the number of the nodes and edges on the performance and
% analyzing its scalability when the size of the datset increases.
% \begin{itemize}
% \item Q1) : Is the runtime affected when more nodes are added?
% \item Q2) : Does it scale to a larger dataset?
% \item Q3) : How does it scale when adding a larger number of datasets?
% \end{itemize}

Comparison of direct mapping vs controlled mapping on the basis of G2GML should be conducted. For several datasets, statistics such as numbers of nodes and edges, and performaces should be presented.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsthm}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
\newtheorem{defi}[theorem]{Definition}
\newtheorem*{prel}{Preliminaries}
%
\title{G2GML: Graph to Graph Mapping Language for Bridging RDF and Property Graphs}
%
\titlerunning{G2GML: Graph to Graph Mapping Lanugage}
%\titlerunning{Interoperable Use of RDF and Property Graph}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Hirokazu Chiba\inst{1} \and Ryota Yamanaka\inst{2} \and Shota Matsumoto\inst{3}}
%
\authorrunning{H. Chiba {\itshape et al.}}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Database Center for Life Science, Chiba 277-0871, Japan\\
\email{chiba@dbcls.rois.ac.jp}
\and
Oracle Corporation, Bangkok 10500, Thailand\\
\email{ryota.yamanaka@oracle.com}
\and
Lifematics Inc., Tokyo 101-0041, Japan\\
\email{shota.matsumoto@lifematics.co.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% The abstract should briefly summarize the contents of the paper in 15--250 words.
How can we maximize the value of accumulated RDF data? Although increasing amounts of scientific and social data are described as RDF, their use cases are still limited. Allowing access to the RDF datasets through various interface beyond the SPARQL interface will be expected. Importing the RDF datasets into various graph analysis engines will increase the values of the datasets.  
However, interoperable management of such graph data is challenging due to the differences in existing models and formats depending on various implementations. Here, we redefine the property graph model incorporating the differences in existing models and propose exchangeable serialization formats for property graphs, which can be converted into specific formats for each of the databases. 
The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
We further propose a framework for mapping RDF graphs to property graphs on the basis of the Graph to Graph Mapping Language (G2GML). Using this framework, accumulated graph data described in RDF can be converted to property graphs, which can then be loaded into several graph database engines for further analysis. 
%This work provides interoperability not only between property graph formats but also between RDF and proper graphs.
%Future works include implementing and utilizing graph algorithms to make the most of the accumulated data in various analytical engines.

@@

The G2GML is a declarative language which consists of pairs of RDF graph patterns and property graph patterns. 
An intuitive meaning of a G2GML description is a map from  RDF subgraphs that matches the specified patterns to specified components of property graphs.

@@

G2GML is a language to describes maps from RDF graphs to Property graphs (PG). G2GML is a domain specific declarative language where programmers only have to describe target patterns of RDF and PG. RDF pattern is described using SPARQL pattern, and PG pattern is described using Cypher pattern.

\begin{prel}
An RDF triple $(s, p, o)$ is an element of $(I \cup B) \times I \times (I \cup B \cup L)$ where $I$, $L$ and $B$ are a set of IRIs, a set of literals and a set of blank nodes, which are considered pairwise disjoint. In this paper, an RDF triple is simply called a triple. For a triple $(s, p, o)$, $s$ is called the subject, $p$ the predicate and $o$ the object. An RDF graph is defined as a finite set of triples.
\end{prel}

\par
In this paper, we call maps written in G2GML as \textit{G2G maps}.
A \textit{G2G map} consists of one or more \textit{node maps} and \textit{edge maps}.
A \textit{node map} is a function that maps from an RDF graph to a set of \textit{PG nodes}. 
Similarly, an \textit{edge map} is a function that maps from an RDF graph to a set of \textit{PG edges}.
The meaning of a G2G map is a function that maps from an RDF graph to a set of PG nodes and edges that is mapped by  all its node and edge maps. We show a complete example of G2GML in Figure \ref{fig:example-g2g}.
%TODO: consider the position of the example
A node map is described as a pair of a PG node pattern  and an RDF graph pattern. Here we define the syntax of PG node pattern as follows. Note that symbols in uppercase are implicitly identifiers.
\begin{defi}[EBNF notation of PG node pattern]
\leavevmode
\begin{verbatim}
 node_pat  ::= "(" NODE  ":" LABEL  ("{" prop_list "}")? ")"
 prop_list ::= property "," prop_list | property
 property  ::= PROP_NAME ":" PROP_VAL
\end{verbatim}
\end{defi}

A PG node pattern specifies a node, a label and properties to be generated by the map. The \texttt{NODE} symbol specifies ID of the generated node, which is replaced by the resource retrieved by RDF graph. The \texttt{LABEL} symbol specifies the label of the resultant node. A label also works as the name of the node map which is referred from edge maps.
Therefore an identifier of a label must be unique in a  G2GML map.
Each node pattern contains zero or more properties as \texttt{prop\_list}.
A \texttt{property} is a pair of \texttt{PROP\_NAME} and \texttt{PROP\_VAL} that describes properties of nodes.
Identifiers \texttt{NODE} and \texttt{PROP\_VAL} must be names of variables in the succeeding RDF graph pattern, while \texttt{LABEL} and \texttt{PROP\_NAME} are regarded as text literals.

An RDF graph pattern in G2GML can be written in \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).
An RDF graph pattern specifies which resources should be mapped to PG nodes. Resources matching with these pattern yield solution sets of SELECT query in SPARQL, which 
 are mapped to PG nodes by embedding variable bindings to corresponding location according to the preceding PG node pattern.
Here, a variable bound to \texttt{PROP\_VAL} may have multiple candidates for single node. If such multiple candidate exists, they are concatenated into an array in the manner of \texttt{GROUP\_CONCAT} in SPARQL if multiple resources are bound to single \texttt{PROP\_NAME}.

A PG edge pattern specifies a pattern of edge, the label, the properties and the source node and the destination node.
Here we define the syntax of PG edge pattern as follows.
\begin{defi}[EBNF notation of PG edge pattern]
\leavevmode
\begin{verbatim}
edge_pat ::= "(" SRC  ":" SRC_LAB ") -" 
                "[" EDGE?  ":" EDGE_LAB  ("{" prop_list "}")? ")" 
                ("->" | "-") "(" DST ":" DST_LAB ")"
\end{verbatim}
\end{defi}

 Identifiers of \texttt{SRC} and \texttt{DST} specify which variables in the succeeding RDF graph pattern should be mapped to endpoint nodes of resultant edges.
A \texttt{SRC\_LAB} and a \texttt{DST\_LAB} work not only as labels of resultant nodes but also work as implicit constraints of the edge map.
%TODO add ref
The resultant source nodes and destination nodes must match patterns in corresponding node maps.
For this reason, \texttt{SRC\_LAB} and \texttt{DST\_LAB} must be defined in other node maps.
\texttt{EDGE}, \texttt{EDGE\_LAB} and \texttt{prop\_list} can be described in the same manner as those counterparts in node maps.

The primary key of an edge map is the tuple of the resources bound to \texttt{SRC}, \texttt{EDGE} and \texttt{DST}. As well as node maps, other values of properties bound in \texttt{prop\_list} are concatenated into an array.

The resultant edges can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge part and a destination part, the edge will be a directed edge.
 %TODO: add whole syntax of G2G using PG node pattern and edge pattern and SPARQL

@@

\begin{defi}[EBNF notation of the PG format]
\leavevmode
\begin{verbatim}
 pg         ::= (node | edge)+
 node       ::= NODE_ID labels properties NEWLINE
 edge       ::= NODE_ID direction NODE_ID labels properties NEWLINE
 labels     ::= label*
 properties ::= property*
 label      ::= ":" STRING
 property   ::= STRING ":" value
 value      ::= STRING | NUMBER
 direction  ::= "--" | "->"
\end{verbatim}
\end{defi}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Use Cases}

We present several use cases to show how to applythe usefulness of G2G mapping framework, where we utilizeuse publicly available open data available in RDF datasets through SPARQL endpoints.

@@

%--code--code--code--code--code--
\begin{figure}[!t]
\vspace{2mm}
\begin{scriptsize}
\begin{verbatim}

@@

\end{verbatim}
\end{scriptsize}
\caption{G2GML for Wikidata extraction}
\label{fig:g2gml_wikidata}
\end{figure}
%--code--code--code--code--code--

@@

@@

\begin{table}[h]
    \centering
    \begin{tabular}{l|r|r|r|r}
        \hline
        & RDF nodes & RDF edges & PG nodes & PG edges \\
        \hline
        Wikidata disease & 20,692 & 36,826 & 10,488 & 11,770 \\
        DBpedia musician & 24,660 &  & 12,329 & 57,351 \\
        \hline
    \end{tabular}
    \caption{Number of nodes and edges}
    \label{tab:my_label}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@
